Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-01 paper.tex
Cite Crivellini2014; resolves #18
Add Balduzzi2016 citation

Computational fluid dynamics (CFD) presents an attractive method for simulating
cross-flow turbines since it only requires turbulence modeling, i.e., the
machine is described from first principles. However, CFD can be computationally
expensive when done in three dimensions, which may be necessary in some cases.
There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results.

@@

In this study we seek to predict the near-wake of the UNH-RVAT turbine,
experimental performance curves for which are shown in
Figure~\ref{fig:exp_perf}. We modeled the turbine at a tip speed ratio
$\lambda=1.9$, which corresponds to the maximum power coefficient.

@@

The flow field was modeled using the Reynolds-averaged Navier--Stokes equations,
employing two different turbulence models---Menter's $k$--$\omega$ SST
\cite{Menter1994} and the Spalart--Allmaras (SA) one equation model
\cite{Spalart1992}. The SST model was chosen due to its prominence in the
literature for simulating separating flows, which we assumed to be present in
the current problem in the form of dynamic stall. The SA model was shown by
Ferreira et al. \cite{Ferreira2007} to match experimental particle image
velocimetry (PIV) results for a CFT in dynamic stall, though this was a somewhat
low Reynolds number case ($5 \times 10^4$).

>>>>

Computational fluid dynamics (CFD) presents an attractive method for simulating
cross-flow turbines (CFTs) since it only requires turbulence modeling, i.e., the
machine is described from first principles. However, CFD can be computationally
expensive when done in three dimensions, which may be necessary in some cases.
There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results. Balduzzi et al. provides a summary of recent
computations and an attempt to standardize a methodology for using
Reynolds-averaged Navier--Stokes (RANS) to correctly simulate performance of a
2-D CFT \cite{Balduzzi2016}.

@@

In this study we seek to predict the near-wake of the UNH-RVAT turbine,
experimental performance curves for which are shown in
Figure~\ref{fig:exp_perf}. We modeled the turbine at a tip speed ratio
$\lambda=1.9$, which corresponds to the maximum power coefficient, and a turbine
diameter Reynolds number $Re_D \approx 10^6$, which corresponds to a
$Re$-independent state for both performance and near-wake characteristics, as
determined from experimental measurements \cite{Bachant2014,
    Bachant2015-RVAT-Re-dep}.

@@

The flow field was modeled using the Reynolds-averaged Navier--Stokes equations,
employing two different turbulence models---Menter's $k$--$\omega$ SST
\cite{Menter1994} and the Spalart--Allmaras (SA) one equation model
\cite{Spalart1992}. The SST model was chosen due to its prominence in the
literature for simulating separating flows, which we assumed to be present in
the current problem in the form of dynamic stall. The SA model was shown by
Ferreira et al. \cite{Ferreira2007} to match experimental particle image
velocimetry (PIV) results for a CFT in dynamic stall, though this was a somewhat
low Reynolds number case ($5 \times 10^4$). Further justification for using the
SA model for this case comes from Crivellini and D'Alessandro
\cite{Crivellini2014}, where they successfully modeled the laminar separation
bubble and subsequent boundary layer transition to turbulence at Reynolds
numbers similar to ours.
